---
title: "Time Series"
author: "bky"
output: html_document
---
#Time Series

The last way of visually representing data is through a time series plot. A time series plot displays values against time. They are similar to x-y graphs, but while an x-y graph can plot a variety of "x" variables (for example, height, weight, age), timeplots can only display time on the x-axis. Unlike pie charts and bar charts, these plots do not have categories. Timeplots are good for showing how data changes over time.

First we will import the necessary packages:
```{r}
library(Lahman)
library(sqldf)
library(devtools)
library(ggplot2)
```

Next we will extract the data:
```{r}
query<-"SELECT yearID,HR FROM Batting WHERE playerID='ruthba01'"

result<-sqldf(query)
```

Last we will visualize the data:
```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR),color="black")+
  geom_line(data=result,aes(x=yearID,y=HR),color="red")+
  ggtitle("Ruth's Homerun Totals Through the Years")+
  xlab("Year")+
  ylab("Homeruns")
```

